---
title: "SLIDE Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SLIDE Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## SLIDE Package

##Description

The SLIDE R package is an implementation of the Single Cell Linkage using Distance Estimation (SLIDE) algorithm (Sen et al), to be used to detect infectious reprogramming of cells in high dimentional flow cytometry data. The package contains one major function, `slide()`, which does the following:
1. Tells us which protein expression levels are significantly up or downregulated in in infected cells compared to uninfected cells
2. Tests for statistically significant evidence for cellular reprogramming under the infectious condition.

## Example

`slide()` requires two dataframes as input, one with protein expression levels for an infected subset of cells, and another with that of uninfected cells. The function returns results as a five item list.

```{r example, eval=FALSE}
## Basic example using the default cutoff
slide(infected = I_sig, uninfected = UN_sig)

## Using bootstrap to determine cutoff, then running SLIDE
cutoff <- bootstrap_cutoff(uninfected = UN_sig, fraction = (nrow(I_sig)/nrow(UN_sig)), iter = 40)
slide(infected = I_sig, uninfected = UN_sig, cutoff = cutoff)

```

## Aknowledgments

The development of this R package was supported by National Science Foundation grant DMS-1811866. 

## References

Sen, N., Mukherjee, G., and Arvin, A.M. (2015). Single cell mass cytometry reveals remodeling of human T cell phenotypes by varicella zoster virus. Methods 90, 85–94.





